%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
 
\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Jeremy}{Brown}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.35\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\degree{Georgia Tech}{Atlanta, Georgia}{BS}{Computer Science}{May 2015}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Languages}

\descript{Over 5000 lines:}
Bash \textbullet{} Python

\descript{Over 1000 lines:}
Java \textbullet{} \LaTeX\

\descript{Familiar:}
C \textbullet{} CSS \textbullet{} Groovy \textbullet{} HTML \\
SQL
\sectionsep

\subsection{Skill Areas}

\descript{Strong:}
Computer Security \\
Systems Administration \\
Network Administration
\sectionsep

\subsection{Tools and Frameworks}
\descript{Strong:}
Git \textbullet{} GitHub \textbullet{} Hypothesis \\
pytest

\descript{Intermediate:}
Flask \textbullet{} Jenkins \textbullet{} Make \textbullet{} MySQL


\descript{OK:}
Android \textbullet{} Gradle \textbullet{} Maven
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\subsection{Anime Weekend Atlanta}
\descript{Staffer of the Year}
\location{Technical/Main Events | Sept 2015}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     CONTACT
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Contact}
\personal
{mischif@users.noreply.github.com}
{}
{mischif}
{}
{}
{}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.64\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\nameandloc{RiVi Consulting}{Atlanta, Georgia}
\titleandtime{Python Developer}{July 2020}{Present}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Designed and implemented microservice development, integration and deployment strategies.
\item Created standards-compliant project templates to decrease learning curve for junior contibutors.
\end{tightemize}
\sectionsep

\nameandloc{Pindrop}{Atlanta, Georgia}
\titleandtime{Software Engineer}{February 2016}{August 2019}
\begin{tightemize}
\item Led efforts to update on-premise appliance codebase to Python 3.
\item Updated entire call analysis pipeline to Python 3.6.
\item Rewrote libraries shared with other teams for cross-version compatibility.
\item Designed and wrote initial telemetry package to monitor SLA adherence. 
\item Migrated call analysis pipeline to local identifiers, solving multiple system-breaking issues at major customers.
\end{tightemize}
\sectionsep

\nameandloc{Microsoft}{Redmond, Washington}
\titleandtime{Software Development Engineer Intern}{May 2014}{August 2014}
\begin{tightemize}
\item Designed protocol to use mobile devices as secure access control tokens.
\item Created reference implementation to test viability in real-world situations.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PRESENTATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Presentations} 
\nameandloc{Georgia Institute of Technology}{Atlanta, Georgia}
\titleandtime{An Introduction to Web Security}{October 23, 2013}{}
\begin{tightemize}
\item A lighthearted exposure to select vulnerability classes from the OWASP Top 10 with potential mitigations.
\item Delivered as part of web security module created by me for introductory graduate information security course.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\subsection{PORTALofPi}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Isolating Tor proxy based on Raspberry Pi and Alpine Linux.
\item Transparently tunnels TCP and DNS traffic over Tor, and exposes SOCKS proxy for tunneling UDP.
\end{tightemize}
\sectionsep

\subsection{py-fast-trie}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Python X-fast trie and Y-fast trie implementations.
\item Searches are log-logarithmic in the size of the defined universe.
\item Insertions/deletions are amortized logarithmic or log-logarithmic depending on structure.
\end{tightemize}
\sectionsep

\subsection{py-hopscotch-dict}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Full-featured replacement for standard Python dict that implements hopscotch hashing.
\item Additions, deletions and lookups have an expected O(1) runtime.
\end{tightemize}
\sectionsep

%\subsection{rstats-logreader}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Python 2/3-compatible utility for reading version 0 and version 1 RStats logfiles.
%\item Supports exporting data to CSV or JSON, plus viewing data by arbitrary week/month groupings.
%\end{tightemize}
%\sectionsep
%
%\subsection{id3autosort}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Python 2/3-compatible utility for organizing music files based on metadata.
%\item Supports most common audio metadata formats.
%\end{tightemize}
%\sectionsep

\subsection{WormySharpyLoggy}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Android pattern-matching game with a focus on casual play.
\item Refactored senior design project to support additional game mode and include greater test coverage.
\end{tightemize}
\sectionsep

%\subsection{BuzzPrint}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
%\begin{tightemize}
%\item Flask webapp providing access to Georgia Tech print queues via the Internet.
%\item Supports printing Google Docs and valid linked/uploaded document types.
%\item Enables mobile devices and Linux computers to use Georgia Tech print queues.
%\end{tightemize}
%\sectionsep

\end{minipage}
\end{document}
